Simulation and visualization framework for decision making of climate mitigation \vspace{4pt} and adaptation strategies in new and existing urban development

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex

%---------------------------------------------------------------------------------------
\section*{Results}
The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic. A final open-database is available in the repository mentioned in the abstract. From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, \ref{fig:MACC_true_noDH}, and \ref{fig:MACC_true_DH}. These are discussed at more in the following sections but differ in that they are constructed following two logics. The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected. The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in Figures \ref{fig:MACC_true_noDH_waterfall} and \ref{fig:MACC_true_DH_waterfall}.

@@

\subsection*{General Performance}
Figure \ref{fig:cross_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios. Three groups tend to emerge with the most start difference being that one group is emitting far more than the other two. This is a result of those scenarios still relying on the natural-gas based heating system. This difference is apparent across both climate change pathways, leading to a conslusion that the impacts of more severe climate are not disrupting mitigation efforts in the model. It appears to enable it to an extent. Comparing the highlighted groups of similar scenarios between the best-case and worst-case scenarios a decrease in lifetime emissions is apparent. We suspect that this is due to the warmer temperatures reducing the heating seasons as well as enabling the district to remain below the heat pump capacity more of the year. Figure \ref{fig:comapre_district} shows this in the operation of the district in the baseline cases from each climate scenario.

@@

\subsection*{Visualizing decision making}
Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario. For each of the four combinations of development and climate change pathway, Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier. The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%. The figure as a whole was created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom row which contains only a single strategy implemented. This format allows us to view the optimal target and then evaluate how to achieve that by selecting strategy combinations in reverse, as suggested by the overlaid pathway. In several cases no optimum set is reached due their only being one optimum. As a decision-making tool these types of graphs allow us to compare two base-metrics for economic decision making about mitigation and the effectiveness of the strategies as adaptation efforts.

MACCs were drawn as another form of visualising decision making. Figure \ref{fig:MACC_budget} is not a \textit{true} MACC in that you can only implement one of the strategy-sets, represented by the bars. However, it improves on previous \textit{illustrative} MACCs in that the bars do not unnecessarily represent single strategy interventions, but rather a set of strategies. It was drawn to assist in planning under the assumption that planners are expecting a worst-case climate change scenario by the end of the century and have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies. The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget, selecting \textit{01011001} at the marginal abatement cost of -\$123. Another \textit{illustrative} MACC was drawn, seen in Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario. All bars represet strategy-sets that would reach that reductions total, ultimately \textit{0111000} is chosen at the marginal abatement cost of -\$50.

@@

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}. Figure \ref{fig:MACC_true_noDH} describes how each strategy contributes to the overall decrease in emissions. The MACC is shown in Figure \ref{fig:MACC_true_noDH} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction. This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity. The majority of the abatement can be attributed to the heat pump strategy, removing natural gas from the fuel mix, while the other strategies can be said to lending to adaptability. This point about the fuel mix will be returned to more in the discussion, but raises that question about how to affordably meet zero-carbon targets after fuel-switching has been achieved. This scenario only achieves 67\% emissions reduction over the baseline by 2080.

@@

A second \textit{true} MACC was generated under the plan to abate as many emissions as possible while continuing to use the district heating system, under the worst-case climate scenario. Figure \ref{fig:MACC_true_DH} describes how each measure contributes to overall emissions reduction. The resulting MACC shows a more consistent scale of MAC and overall abatement between measures that the previous example, but total abatement is only 8\% of the baseline's emissions.

@@

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=0.55]{figures/pareto_plots_585.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:pareto_plot}
\end{figure}

@@

The resulting MACCs were created from two perspectives. First the \textit{illustrative} MACCs (Figures \ref{fig:MACC_threshold} and \ref{fig:MACC_budget}) provide general guidance on choosing sets of strategies to achieve mitigation under different planning constraints. The \textit{true} MACCs (Figures \ref{fig:MACC_true_DH} and \ref{fig:MACC_true_noDH}) reveal how the individual strategies within a set interact to technically and financially to ultimately abate a certain amount of carbon. The candidate for the one of the \textit{true} MACCs was selected based on a mixture of adaptation and mitigation criteria using a plot of pareto optimums (Figure \ref{fig:pareto_plot}). This enables planners to begin to assess adaptation targets alongside abatement.

>>>>

%---------------------------------------------------------------------------------------
\section*{Results}
The simulation procedure was executed for 1024 scenarios, producing hourly demand results for each building within the simulation space, as well as annual cost and emissions results for each building. For iterations in which rooftop-photovoltaic was an option a set of results was generated to be used in correcting total grid-demand for the electricity generated by the rooftop-photovoltaic. A final open-database is available in the repository mentioned in the abstract. From these iterations several MACCs were constructed in Figures \ref{fig:MACC_budget}, \ref{fig:MACC_threshold}, and \ref{fig:true_macc_both}. These are discussed at more in the following sections but differ in that they are constructed following two logics. The first two are \textit{illustrative} MACCs in that they present a set of possible interventions, but not necessarily a pathway through which those interventions can be connected. The latter two are \textit{true} MACCs in that each bar represents a singular strategy where the MAC considers the economic and technical impacts of the other presented strategies and those that may be included in the strategy set but are not included in the MAC, as they do not abate carbon by themselves, as seen in the first and third frame of Figure \ref{fig:true_macc_both}.

@@

\subsection*{General Performance}
Figure \ref{fig:cross_plot} displays net-cost and gross emissions for each iteration within each of the four scenarios. Three groups tend to emerge with the most start difference being that one group is emitting far more than the other two. This is a result of those scenarios still relying on the natural-gas based heating system. This difference is apparent across both climate change pathways, leading to a conclusion that the impacts of more severe climate are not disrupting mitigation efforts in the model. It appears to enable it to an extent. Comparing the highlighted groups of similar strategy-sets between the best-case and worst-case scenarios a decrease in lifetime emissions is apparent. We suspect that this is due to the warmer temperatures reducing the heating seasons as well as enabling the district to remain below the heat pump capacity more of the year.

% Figure \ref{fig:comapre_district} shows this in the operation of the district in the baseline cases from each climate scenario.

@@

\subsection*{Visualizing decision making}
MACCs were drawn as another form of visualising decision making. Figure \ref{fig:MACC_budget} is not a \textit{true} MACC in that you can only implement one of the strategy-sets, represented by the bars. However, it improves on previous \textit{illustrative} MACCs in that the bars do not unnecessarily represent single strategy interventions, but rather a set of strategies. It was drawn to assist in planning under the assumption that planners are expecting a worst-case climate change scenario by the end of the century and have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies. The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget, selecting \textit{01011001} at the marginal abatement cost of -\$123. Another \textit{illustrative} MACC was drawn, seen in Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario. All bars represet strategy-sets that would reach that reductions total, ultimately \textit{0111000} is chosen at the marginal abatement cost of -\$50.

@@

Marginal abatement cost and the adaptation metric were plotted to evaluate the Pareto front of each scenario. For each of the four combinations of development and climate change pathway, Figure \ref{fig:pareto_plot} highlights the best performing set of experiments using a convex hull, pareto frontier. The adaptation metric is altered in these plots to show the remaining percentage of \textit{hours outside of the threshold}, where the optimum would be 0\%. The figure as a whole was created under that assumption that only one strategy can be implemented at a time, with the topmost row containing all 255 experiments for each scenario and the following rows one less strategy implemented until the bottom row which contains only a single strategy implemented. These charts can inform the creation of a \textit{true} MACC by informing which strategy set is chosen based on not only marginal abatement cost, but also the adaptation metric.

Of the two \textit{true} MACCs used in this study, the first represents a strategy-set that was chosen based on a high degree of adaptability present, while also abating a large amount of emissions. This was done under the worst-case climate scenario and the selected strategy-set \textit{00011111} is highlighted in Figure \ref{fig:pareto_plot}. Figure \ref{fig:true_macc_both} describes how each strategy contributes to the overall decrease in emissions. The MACC is shown in Figure \ref{fig:true_macc_both} where the first strategy, the installation of heat pumps in all buildings to service space heating and cooling as well as domestic hot water, contributes to the bulk of the emissions reduction. This is due to the impact that moving away from the district heating system, which has the potential to use natural gas if heating and DHW load exceeds the district's heat pump capacity. The majority of the abatement can be attributed to the heat pump strategy, removing natural gas from the fuel mix, while the other strategies can be said to lending to adaptability. This point about the fuel mix will be returned to more in the discussion, but raises that question about how to affordably meet zero-carbon targets after fuel-switching has been achieved. This scenario only achieves 67\% emissions reduction over the baseline by 2080.

@@

A second \textit{true} MACC was generated under the plan to abate as many emissions as possible while continuing to use the district heating system, under the worst-case climate scenario. Figure \ref{fig:true_macc_both} describes how each measure contributes to overall emissions reduction. The resulting MACC shows a more consistent scale of MAC and overall abatement between measures that the previous example, but total abatement is only 8\% of the baseline's emissions.

@@

\begin{figure}[t]
    \centering
    \captionsetup{margin=.5cm}
    \includegraphics[scale=0.50]{figures/pareto_plots_585_box.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:pareto_plot}
\end{figure}

@@

The resulting MACCs were created from two perspectives. First the \textit{illustrative} MACCs (Figures \ref{fig:MACC_threshold} and \ref{fig:MACC_budget}) provide general guidance on choosing sets of strategies to achieve mitigation under different planning constraints. The \textit{true} MACCs (Figure \ref{fig:true_macc_both}) reveal how the individual strategies within a set interact to technically and financially to ultimately abate a certain amount of carbon. The candidate for the one of the \textit{true} MACCs was selected based on a mixture of adaptation and mitigation criteria using a plot of pareto optimums (Figure \ref{fig:pareto_plot}). This enables planners to begin to assess adaptation targets alongside abatement.
